H52F-05H: Robust Adaptation to\\Multi-Scale Climate Variability

### 2018-12-11 slides-agu/presentation.tex
Update draft of slides for AGU

\begin{frame}{Thanks to...}
  \begin{itemize}
    \item Co-authors
    \begin{itemize}
      \item Upmanu Lall
      \item David J. Farnham
      \item Scott Steinschneider
    \end{itemize}
    \item Funders
    \begin{itemize}
      \item NSF GRPF
      \item Columbia University Fu Foundation SEAS
      \item DoD SERDP
    \end{itemize}
    \item Conveners, colleagues, collaborators
  \end{itemize}
\end{frame}

\begin{frame}{Motivating Example}
  \begin{columns}[T]
    \pause
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \centering
        \caption{
          Permanent structural solution would pose environmental and social impacts and lock in $\approx \$25 \text{billion}$;
          a portfolio of smaller projects may allow a more flexible strategy.
        }
        \includegraphics[width=0.85\columnwidth]{three-barriers.png}\\
        \includegraphics[width=0.85\columnwidth]{flood-concept.png}
      \end{figure}
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item ``Because present decisions impact a system's ability to adapt to future needs, flexibility in activating, delaying, and replacing engineering projects should be considered in least‐cost water supply intervention scheduling,'' \citep{erfani:2018}.
        \item How to build a portfolio of risk management investments, over time, given uncertain future climate/society/technology?
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Idea 1: Risk Estimates over Finite Future Periods}
  \begin{alertblock}{Typical Approach:}
    \gls{cba}, probably with discounting, over a \alert{finite} planning horizon of $M$ years (explicitly or implicitly).
  \end{alertblock}
  \begin{columns}
    \pause
    \begin{column}{0.5\textwidth}
      Thus, evaluation of project depends on climate conditions over the next $M$ years:
      \begin{itemize}
        \item For ``mega-project'', $M \geq \SI{50}{years}$
        \item For small, flexible project, $M \leq \SI{5}{years}$
      \end{itemize}
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      Misrepresentation of climate risk over $M$ years $\rightarrow$ bias in \gls{cba}
      \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio=true]{Bias-Variance-Sketch}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Idea 2: Physical Drivers of Risk Depend on $M$}
  The physical drivers of hazard depend on the projection horizon ($M$).
  \begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth,keepaspectratio=true]{conceptual-sketch-a.png}\\
  \end{figure}
  \pause
  However, our ability to identify these mechanisms depends on information available (\eg, the length of an $N$-year observational record).
  \begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth,keepaspectratio=true]{conceptual-sketch-b.png}
  \end{figure}
\end{frame}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How well can one identify and predict risk}
     associated with cyclical and secular climate signals over a finite design life ($M$),  given limited information (\eg, an $N$-year record).
  \end{alertblock}
  \pause
  In particular, we consider:
  \begin{itemize}
    \item the specific roles of $M$ and $N$;
    \pause
    \item estimation strategy (few processes/parameters $\Rightarrow$ many processes/parameters)
    \pause
    \item the form of the underlying climate signal.
  \end{itemize}
  \pause
  Use simplest possible representation of key processes.
\end{frame}

@@

\begin{frame}{Summary}
  Starting point:
  \begin{enumerate}
    \item Investment evaluation depends on climate condition over finite planning period
    \item Physical drivers of risk depend on planning period
  \end{enumerate}
  \pause
  As a consequence:
  \begin{itemize}
    \item \emph{Ability} to identify and predict different climate signals depends on information available (\eg, $N$)
    \item \emph{Importance} of identifying and predicting different climate signals depends on degree of extrapolation desired (\ie, $M$)
  \end{itemize}
  \pause
  In general, low risk tolerance and/or short $N$ favor short-$M$ investments relative to long-$M$ ones.
\end{frame}

@@

\begin{frame}{Real-World Climate Signals}
  Real-world hydroclimate systems vary on many time and space scales
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth]{observed-lfv.pdf}
    \caption{
      (a) \SI{500}{year} reconstruction of summer rainfall over Arizona from LBDA \citep{Cook:2010bz}.
      (b) A \SI{100}{year} record of annual-maximum streamflows for the American River at Folsom.
      (c),(d): wavelet global (average) spectra.
    }\label{fig:observed-lfv}
  \end{figure}
\end{frame}

>>>>

\begin{frame}{Motivating Example \citep{CityofNewYork:2013uh}}
  \begin{columns}[T]
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\columnwidth]{three-barriers.png}
        \caption{
          Large, permanent project would lock in $\approx \$25 \text{billion}$ for fixed protection.
        }
      \end{figure}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\columnwidth]{flood-concept.png}
        \caption{
          A sequenced portfolio of smaller investments may be more flexible and adaptive.
        }
      \end{figure}
    \end{column}
  \end{columns}
  \begin{alertblock}{Scheduling and sequencing:}
    \alert{If} and \alert{when} to build the permanent project?
  \end{alertblock}
\end{frame}

@@

\begin{frame}{Idea 1: Risk Estimates over Finite Future Periods}
  \begin{alertblock}{Typical Approach:}
    \gls{cba}, probably with discounting, over a \alert{finite} planning horizon of $M$ years (explicitly or implicitly).
  \end{alertblock}
  \pause
  Project should be evaluated on climate conditions over this finite planning period:
  \begin{itemize}
    \item For ``mega-project'', $M \geq \SI{50}{years}$
    \item For small, flexible project, $M \leq \SI{5}{years}$
  \end{itemize}
\end{frame}

\begin{frame}{Idea 2: Hydroclimate Systems Vary on Many Scales}
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth]{observed-lfv.pdf}
    \caption{
      (a) \SI{500}{year} reconstruction of summer rainfall over Arizona from LBDA \citep{Cook:2010bz}.
      (b) A \SI{100}{year} record of annual-maximum streamflows for the American River at Folsom.
      (c),(d): wavelet global (average) spectra.
    }\label{fig:observed-lfv}
  \end{figure}
\end{frame}

\begin{frame}{Idea 3: Physical Drivers of Risk Depend on $M$}
  The physical drivers of hazard depend on the projection horizon ($M$),
  \begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth,keepaspectratio=true]{conceptual-sketch-a.png}\\
  \end{figure}
  \pause
  but our ability to identify these mechanisms depends on information available (\eg, the length of an $N$-year observational record).
  \begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth,keepaspectratio=true]{conceptual-sketch-b.png}
  \end{figure}
\end{frame}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How well can one identify and predict risk}
     associated with cyclical and secular climate signals over a finite design life ($M$),  given limited information (\eg, an $N$-year record).
  \end{alertblock}
  \pause
  In particular, we consider:
  \begin{itemize}
    \item the specific roles of $M$ and $N$;
    \pause
    \item estimation strategy (few processes/parameters $\Rightarrow$ many processes/parameters)
    \pause
    \item the form of the underlying climate signal.
  \end{itemize}
  \pause
  Use parsimonious representation of key processes.
\end{frame}

@@

\begin{frame}{Summary}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      Assertions:
      \begin{enumerate}
        \item Investment evaluation depends on climate condition over finite planning period
        \item Physical hydroclimate systems vary on many scales
        \item Physical drivers of risk depend on planning period
      \end{enumerate}    
    \end{column}
    \begin{column}{0.5\textwidth}
      Implications:
      \begin{itemize}
        \item \emph{Ability} to identify and predict different climate signals depends on information available (\eg, $N$)
        \item \emph{Importance} of identifying and predicting different climate signals depends on degree of extrapolation desired (\ie, $M$)
        \item In general, low risk tolerance and/or short $N$ favor short-$M$ investments relative to long-$M$ ones.
      \end{itemize}    
    \end{column}
  \end{columns}
\end{frame}

@@
